### 2021-12-24 chapters/02-chapter-2.tex
txs auto checkin

\begin{small}
	\begin{longtable}{ | p{5cm} | p{2cm} | p{2cm} | p{2cm} | }
		\caption{Rata-rata durasi \textit{span} dalam \textit{trace} \textit{baseline} dan regresi}
		\label{corr-tab-3}                                                           
		\\ \hline
		\centering\bfseries{\textit{Tag}} & \centering\bfseries{\textit{Baseline}} & \centering\bfseries{Regresi} & \centering\bfseries{Perubahan} \tabularnewline \hline
		\endfirsthead
		\textbf{item-type}: new & 114 ms & 1240 ms & +1130 ms \\ \hline
		\textbf{client.browser}: mozilla68 & 111 ms & 548 ms & +437 ms \\ \hline
		\textbf{db.instance}: cassandra.4 & 117 ms & 464 ms & +348 ms \\ \hline
		inventory/update-inventory & 15.2 ms & 14.8 ms & $\num{-0.47}$ ms \\ \hline
		inventory/database-update & 32 ms & 30.6 ms & $\num{-1.4}$ ms \\ \hline
	\end{longtable}
\end{small}

>>>>

\begin{small}
	\begin{longtable}{ | p{5cm} | p{2cm} | p{2cm} | p{2cm} | }
		\caption{Rata-rata durasi \textit{span} dalam \textit{trace} \textit{baseline} dan regresi}
		\label{corr-tab-3}                                                           
		\\ \hline
		\centering\bfseries{\textit{Tag}} & \centering\bfseries{\textit{Baseline}} & \centering\bfseries{Regresi} & \centering\bfseries{Perubahan} \tabularnewline \hline
		\endfirsthead
		\textbf{item-type}: new & 114 ms & 1240 ms & +1130 ms \\ \hline
		\textbf{client.browser}: mozilla68 & 111 ms & 548 ms & +437 ms \\ \hline
		\textbf{db.instance}: cassandra.4 & 117 ms & 464 ms & +348 ms \\ \hline
		\textbf{runinfo.host}: vm123 & 115 ms & 453 ms & +337 ms \\ \hline
	\end{longtable}
\end{small}
